Quantifying maternal reproductive output of chondrichthyan fishes

### 2024-09-23 README.qmd
readme

Load data for sandbar shark maternity data set. Rows are data from individuals sharks x is fork length (cm) and z is maternal status (0 = non maternal, 1 = maternal).

@@

data %>% 
  ggplot() + 
  geom_histogram(aes(x = x, fill = as.factor(z)), binwidth = 5, col = "black") +
  labs(x = "Fork length (cm)", y = "Proportion in maternal condition") + 
  guides(fill = guide_legend(title = "Maternal stage")) + 
  theme(legend.position = "top")

@@

Bin data into suitable length categories for plotting.

```{r message=FALSE, warning=FALSE}
brks = seq(40, 220, 10)
data_binned <- data %>%
  mutate(x_bin = findInterval(x, brks)) %>% 
  mutate(x_bin = (brks[x_bin] + brks[x_bin + 1]) / 2) %>% 
  group_by(x_bin) %>%
  summarise(p = sum(z)/ n())

ggplot()  + 
  geom_point(data = data_binned, aes(x = x_bin, y = p), col = "black") + 
  ylim(0, 1) +
  labs(x = "Fork length (cm)", y = "Proportion in maternal condition")
```

Add marginal rug plots to show individual data points.

```{r}
ggplot()  + 
  geom_rug(data = filter(data, z == 1), aes(x = x), sides = "t") +
  geom_rug(data = filter(data, z == 0), aes(x = x), sides = "b") +
  geom_point(data = data_binned, aes(x = x_bin, y = p), col = "black") + 
  ylim(0, 1) +
  labs(x = "Fork length (cm)", y = "Proportion in maternal condition")

@@

>>>>

Load sandbar shark maternity data set. Rows are data from individuals sharks.

@@

@@

*x* is fork length (cm) and *z* is maternal status (0 = non maternal, 1 = maternal).

```{r}
head(data)
```

```{r}
data %>% 
  ggplot() + 
  geom_histogram(aes(x = x, fill = as.factor(z)), binwidth = 5, col = "black") +
  labs(x = "Fork length (cm)", y = "Proportion in maternal condition") + 
  guides(fill = guide_legend(title = "Maternal stage")) + 
  theme(legend.position = "top")

@@

Bin data into suitable length categories for plotting. Add marginal rug plots to show individual data points.

```{r message=FALSE, warning=FALSE, include=TRUE}
brks = seq(40, 220, 10)
data_binned <- data %>%
  mutate(x_bin = findInterval(x, brks)) %>% 
  mutate(x_bin = (brks[x_bin] + brks[x_bin + 1]) / 2) %>% 
  group_by(x_bin) %>%
  summarise(p = sum(z)/ n())

ggplot()  + 
  geom_rug(data = filter(data, z == 1), aes(x = x), sides = "t") +
  geom_rug(data = filter(data, z == 0), aes(x = x), sides = "b") +
  geom_point(data = data_binned, aes(x = x_bin, y = p), col = "black") + 
  ylim(0, 1) +
  labs(x = "Fork length (cm)", y = "Proportion in maternal condition")
```

### 2024-09-23 rmds/figures.Rmd
changes
readme

---
output: 
  pdf_document:
    latex_engine: "pdflatex"
---

@@

```{r fig.width = 7, fig.height= 5.5}
data <- read_rds(here("data", "simulations-pivot.Rds")) %>% 
  filter(method_long %in% "3PLF - estimated")

>>>>

---
output: 
  pdf_document:
    keep_tex: true
    latex_engine: "pdflatex"

---

@@

```{r fig.width = 7.2, fig.height= 5.5}
data <- read_rds(here("data", "simulations-pivot.Rds")) %>% 
  filter(method_long %in% "3PLF - estimated")
